### 2024-09-10 README.Rmd
continue documentation

### Input Data
The following conditions of an input data frame for any species must be met:
1. (length data) There exists a WEIGHT1 column that represents the haul-level proportions-at-length of the observed lengths. This is calculated by dividing the frequency of the observed length within a haul by the total number of fish lengthed in that haul. It should be a standard calculation that is exactly the same for every species.

@@

>>>>

### Input Data
The following conditions of an input data frame for any species must be met:
1. (length data) There exists a WEIGHT1 column that represents the haul-level proportions-at-length of the observed lengths. This is calculated by dividing the frequency of the observed length within a haul by the total number of fish lengthed in that haul. It should be a standard calculation that is exactly the same for every species. This convention...

2. Length data be condensed with sum_frequency column.

3. Age data include associated lengths.

4. Age data flattened, no "sum_frequency" column.

@@

1. Length ISS must be a separate analysis to age ISS. Unlike surveyISS, this is necessary for several reasons: a. there will be many more hauls with lengths than ages, b. it is likely that the user options such as post_stratify will be different between length data and age data, c. NOTE ANOTHER ONE WHEN YOU REMEMBER.
